Reflections from reproductions

### 2024-10-25 pages/reflections.qmd
docs(reflections): add summary chart + johnson (both W.I.P.)

---
title: "Reflections from reproductions"
bibliography: ../references.bib
---

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | 🟡 | ❌ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | 🟡 | 🟡 |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

>>>>

---
title: "Reflections from reproductions"
echo: False
bibliography: ../references.bib
---

@@

## Summary

<!--TODO: Add stacked bar summary chart -->

```{python}
import pandas as pd
from functions import eval_chart

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'List packages': [2, 3, 3, 0],
  'Provide versions': [0, 6, 2, 0],
  'Model in "runnable" format': [7, 0, 1, 0],
  'Run programmatically': [0, 0, 0, 0],
  '''Don't hard code scenario param.''': [0, 0, 0, 0],
  'Relative file paths': [0, 0, 0, 0],
  'Avoid duplication': [0, 0, 0, 0],
  'Sufficient comments': [0, 0, 0, 0],
  'Quicker (?)': [0, 0, 0, 1],
  'If slow, state run time': [0, 0, 0, 0],
  'If comp. exp., state usage + alt.': [0, 0, 0, 0],
  'Provide scenario code': [0, 0, 0, 0],
  'Provide all required outputs': [0, 0, 0, 0],
  'Include correct parameters': [0, 0, 0, 0],
  'Provide all required parameters': [0, 0, 0, 0],
  'If not, clearly state in paper': [0, 0, 0, 0],
  'If process param., provide calc.': [0, 0, 0, 0],
  'Save output to file': [0, 0, 0, 0],
  'Understandable output tables': [0, 0, 0, 0],
  'Avoid large files (?)': [0, 0, 0, 1],
  'Not excessive output files': [0, 0, 0, 0],
  'Use seeds': [0, 0, 0, 0],
  'Code to make tables': [0, 0, 0, 0],
  'Code to make figures': [0, 0, 0, 0],
  'Code to process in-text results': [0, 0, 0, 0],
  'Run instructions': [0, 0, 0, 0],
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

eval_chart(criteria_wide)
```

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | 🟡 | 🟡 | ❌ |

@@

@johnson_cost_2021: Partially met. `DESCRIPTION` file accompanying `epicR` package contained some but not all dependencies.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |

@@

@johnson_cost_2021: Partially met. R version given in paper. `DESCRIPTION` file contains minimum versions for some but not all packages.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
